Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-09-12 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

\section{Designs Considered}
In this study, we focus on four different lattice configurations constrained to deform in an in-plane setting only. In an effort to provide a fair performance compassion between the different designs all of the respective lattice configurations, the total amount of material (i.e. volume or mass) is conserved. Moreover,  we consider a fixed volume ratio between non-diagonal and diagonal elements (chosen to match the sponge geometry) and two different shapes for the cross section of all lattice members: circular and rectangular.  For circular cross-sections  we stay consistent with the geometry found within the biological species. However, since slender members with circular cross section easily buckle out-of-plane when the structure is subjected to compression we must mitigate the issue by pursuing a plane-strain structure such that it's depth slenderness ratio is sufficiently deep to avoid out-of-plane buckling. In order to address this, we converted the biological observations of the cylindrical cross-section into a polygonal section. For this new cross-section type, we assume the structure to be sufficiently deep in plane in comparison the structural length scale (plane strain assumption) to avoid out of plane deformation. The out-of-plane slenderness is scaled accordingly with mass to maintain the depth across all elements constant. To the determine the minimum cross-section depth a parametric simulation on depth was run to determine the necessary depth for each structure. The overall minimum depth for all geometries was chosen an a factor of safety of 1.5 was chosen for the finial depth.

@@

For the optimization portion of the work presented in the main article we used a stochastic, derivative-free evolutionary method called Covariance Matrix Adaptation Evolution Strategy (CMA-ES) implementation in Python \citep{hansen2003}. The algorithm input variables are: the structure's mass ratio $\lambda$ (keeping the total structure volume constant, as well as distributing the mass evenly through all diagonal and non-diagonal elements respectively) and the separation of the even numbered diagonal elements from the non-diagonal junction. Separate instances of the optimization algorithm are analyzed for different numbers of diagonal reinforcements. For simulations with odd number of diagonal reinforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry.

For the optimization results presented in the main article, the critical buckling load is the target response maximized. However, a an equivalent analysis is performed to maximize the critical buckling strain as the target response. This analysis is presented in \cref{BucklingOptimization}. Similarly, the same analysis was performed on the elastic stiffness of the structure and yields a trivial result leading to maximizing the allocation of mass to the non-diagonal elements through the mass ratio.

>>>>

\section{Designs Considered}
In this study, we focus on four different lattice configurations constrained to deform in an in-plane setting only. In an effort to provide a fair performance compassion between the different designs all of the respective lattice configurations, the total amount of material (i.e. volume or mass) is conserved. Moreover,  we consider a fixed volume ratio between non-diagonal and diagonal elements (chosen to match the sponge geometry) and two different shapes for the cross section of all lattice members: circular and rectangular.  For circular cross-sections  we stay consistent with the geometry found within the biological species. However, since slender members with circular cross section easily buckle out-of-plane when the structure is subjected to compression we must mitigate the issue by pursuing a plane-strain structure such that it's depth slenderness ratio is sufficiently deep to avoid out-of-plane buckling. In order to address this, we converted the biological observations of the cylindrical cross-section into a polygonal section. For this new cross-section type, we assume the structure to be sufficiently deep in plane in comparison the structural length scale (plane strain assumption) to avoid out of plane deformation. The out-of-plane slenderness is scaled accordingly with mass to maintain the depth across all elements constant. A parametric simulation on depth was analyzed to determine the minimum cross-section depth required to prevent out-of-plane buckling. Once the overall minimum depth for all geometries was chosen a factor of safety of 1.5 was added for the finial depth. The approach for minimum out-of-plane depth was further verified experimentally and the value was determined sufficient.

@@

For the optimization portion of the work presented in the main article we used a stochastic, derivative-free evolutionary method called Covariance Matrix Adaptation Evolution Strategy (CMA-ES) implementation in Python \citep{hansen2003}. The algorithm input variables are: the structure's mass ratio $\lambda$ (keeping the total structure volume constant, as well as distributing the mass evenly through all diagonal and non-diagonal elements respectively) and the separation of the even numbered diagonal elements from the non-diagonal junction. Separate instances of the optimization algorithm are analyzed for different numbers of diagonal reinforcements. For simulations with odd number of diagonal re-enforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry.

For the optimization results presented in the main article, we seek to maximize the singly objective target function for the critical buckling load. However, an equivalent analysis is performed to maximize the critical buckling strain as the target response. This analysis is presented in \cref{BucklingOptimization}. Similarly, the same analysis was performed on the elastic stiffness of the structure and yields a trivial result leading to maximizing the allocation of mass to the non-diagonal elements through the mass ratio.
